DS Tuc b is Aligned?

### 2019-09-20 paper/main.tex
Updates from Overleaf

Planets around young stars are important and valuable. They teach us about planet formation.

@@

@@

@@

@@

Oblateness - how oblate is the star anyway?
Not important for these systems, just infer a different orbital velocity or radius, depending on how its fit. The only place to learn a difference is in ingress/egress, which needs to be resolved at a high timescale. Need a precise stellar radius and eccentricity, at which point it might be useful! But this is hard for these s

Differential rotation not mentionable unless system hystems already.ighly misaligned. Even then the signal is smaller than the scatter due to starspots so many observations will be required to disentangle.

@@

We thank \btmtodo{people} for \btmtodo{things}.

@@

\software{%
    numpy \citep{numpy},
    matplotlib \citep{matplotlib},
    scipy \citep{Jones01}
    astropy \citep{Astropy18},
    eleanor \citep{Feinstein19},
    starry \citep{Luger19},
    theano
    }

\facility{TESS, Magellan:Clay (Planet Finder Spectrograph)}

>>>>

Planet formation is poorly understood \citep[e.g.][]{Morbidelli16}. 
Each discovered planetary system represents an outcome of the planet formation process, and therefore provides an opportunity to learn about how different planets form in different environments. 
However, each observed present-day system is not a pure laboratory: over billions of years, planet-planet and planet-star gravitational interactions can scatter, torque, migrate, or otherwise perturb orbits, distancing planetary systems from their formation state \citep{Kozai62, Lidov62, Fabrycky07, Chatterjee08}. 
This picture is complicated by the fact that in many cases, stellar ages are very poorly known \citep[e.g.][]{Barnes07, Soderblom10}.

Planets in young clusters are valuable resources to provide cleaner test cases. Dynamical interactions like the Kozai-Lidov effect can, depending on the system architecture, occur over hundreds of millions or billions of years \citep{Montet15c, Naoz16}. 
For systems with younger ages, we can rule out certain dynamical interactions, meaning it is likely that the orbit of the planet traces the orbit of the now-dissipated disk.

The orientations of protoplanetary disks relative to the spin of their host stars provide information about the formation of hot Neptunes and hot Jupiters.
The origins of hot Jupiters are still unclear \citep{Dawson18}.
Kozai-Lidov cycles and tidal friction are often invoked to explain the formation of hot Jupiters \citep{Fabrycky07}, but smooth disk migration provides a reasonable alternative in many cases \citep{Ida08}. 
It is possible that multiple channels are required in order to explain all of the observed systems: \citet{Nelson17} analyze data from the HAT and WASP exoplanet surveys and find the data can be well-fit by a model in which $\sim85\%$ of hot Jupiters are formed through high-eccentricity migration and $\sim15\%$ through disk migration.

Disk migration

@@

\subsection{Likelihood Function}

Something in the models subsubsection about Halpha being less noisy than Shk for this star. Probably because of the wavelengths we're dealing with?

@@

\subsection{Asas-sn data to characterize spots}

@@

But cite Barragan, Aigrain here as the power of RVs in mitigating stellar activity.

@@

Oblateness - how oblate is the star anyway?
Not important for these systems, just infer a different orbital velocity or radius, depending on how its fit. The only place to learn a difference is in ingress/egress, which needs to be resolved at a high timescale. Need a precise stellar radius and eccentricity, at which point it might be useful! But this is hard for these systems because orbits are hard for these young systems.

cite \citet{Giminez06} in this section probably.

Differential rotation not measureable unless system highly misaligned. Even then the signal is smaller than the scatter due to starspots (1 m/s for a system like this one) so many observations at high SNR will be required to disentangle. This is going to be tough!

Could we say something about differential rotation from multiple planets? This seems at odds with the previous graph. Maybe in idealized cases? Need to work through this consideration!

Somewhere: \citet{Oshagh18} on limitations of R-M for very active stars.

@@

We thank \btmtodo{people including Michael Gully-Santiago and Leslie Rogers} for \btmtodo{things}.

@@

\software{%
    numpy \citep{numpy},
    matplotlib \citep{matplotlib},
    scipy \citep{Jones01}
    astropy \citep{Astropy18},
    eleanor \citep{Feinstein19},
    starry \citep{Luger19},
    emcee \citep{Foreman-Mackey12}
    }

\facility{Magellan:Clay (Planet Finder Spectrograph), TESS}
